Separation of an upwelling current bounding the Juan de Fuca Eddy

### 2023-05-25 R1/ResponseReviewers.tex

\begin{reply}
    We hadn't defined the interpolation, so added a sentence:
    \begin{lstlisting}
        These lines are made with a two-dimensional interpolation where MVP
        casts at a given depth are given a Gaussian weight $w = \exp^{-(r/r_0)^2}$,
        where $r$ is the distance from the line and $r_0 = 1.5\ \mathrm{km}$.
    \end{lstlisting}
\end{reply}

@@

\begin{point}
    303-304: Is the distribution indicative of substantial isopycnal and vertical mixing, or rather are the sharp cut-offs in $\theta-S$ properties what is indicative of mixing?
\end{point}

\begin{reply}
    The sharp distinction of t-s properties are indicative of mixing. Changed to ``These distinct $\theta$--$S$ properties''.
\end{reply}

\begin{point}
    313-315, 316-318: Neither of these features is apparent to the reader (at least this one!). I see pink at 25.5 and 26.6 kg/m3 but not 26.4 kg/m3.
\end{point}

\begin{reply}
    That is unfortunate because it is one of the main points of the paper!    The new version of Fig 12 has all the data, which we probably should have used in the original version because hopefully it makes the tongue more clear.  We also now refer to this panel explicitly in the text.  We could annotate it, but the plot is already relatively dense.
\end{reply}

@@

\begin{point}
    Figure 11: an arrow along direction of transport would be helpful in addition to the numbers in 11b.
\end{point}

\begin{reply}
    Thanks, done. We also changed the km markings to the turn locations and added ticks on panel d corresponding to the tick locations.
\end{reply}

@@

\begin{point}

    Figure 12: Which data set is this? Worth including in caption and maybe text also.
\end{point}

\begin{reply}
    Fixed; it was the MVP data, though the previous version was a subsample of the full dataset.
\end{reply}

@@

\begin{point}
    338: is advection demonstrated or suggested?
\end{point}

\begin{reply}
    Thanks, ``suggesting'' is definitely better here.
\end{reply}

@@

\begin{reply}
    Thanks; changed as suggested.
\end{reply}

\begin{point}

    393: Is this explicitly shown on a T/S diagram? Perhaps plucking out profiles through the eddy for comparison can make this point more cleanly. Is there preferential warming within the eddy relative to other water masses?
\end{point}

\begin{reply}
    Yes, but perhaps better shown in Fig 3e, k, which are now explicitly referenced here.
\end{reply}

@@

\begin{point}
    414: wording?
\end{point}

\begin{reply}
    Fixed (hopefully) to
    \begin{lstlisting}
        In this calculation, the T-S relationship does not approach
        a straight line until after approximately 60-100 days, or
        until the mixing affects a vertical length scale of
        $\lambda = \left(\tau \kappa\right)^{1/2} \gtrapprox 70\,
        \mathrm{m}$.
    \end{lstlisting}
\end{reply}

\begin{point}
    468: How is this value chosen?
\end{point}

\begin{reply}
    This was just a typical weak coastal current scaling.  We now cite Thomson and Kassovski (2015), and point out that this current could be substantially stronger.
\end{reply}
